 \documentclass[10pt,a4paper,headinclude=true,twoside]{report}
\usepackage[latin1]{inputenc}
\usepackage[a4paper]{geometry}
\usepackage{a4wide}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{pdflscape} % dlia landscape orientation 
\hypersetup{colorlinks,citecolor=black,filecolor=black,linkcolor=black,urlcolor=black}
\usepackage{float}
\usepackage{setspace}
\usepackage{titlesec}
\titleformat{\chapter}
  {\Large\bfseries} % format
  {}                % label
  {0pt}             % sep
  {\huge}           % before-code

\usepackage{fancyhdr}
\pagestyle{fancy}

\fancyhead[LE,RO]{\slshape  \rightmark} %should be used with "twoside" in documentcalss. Delat headeri kak v knigah: vneshnije storoni sovpadajut drug s drugom. 
\fancyhead[LO,RE]{\slshape  \leftmark}
\fancyfoot[C]{\thepage}
\lhead{}
\rhead{SE31520 Assignment: Enhancing the CS-Alumni Application}

\renewcommand{\familydefault}{\sfdefault}

\begin{document}
\title{SE31520: Car Insurance System}
\author{Edgar Ivanov\\ edi@aber.ac.uk \\ Department of Computer Science, Aberystwyth University}
\date{\today}
\maketitle

\newpage
\thispagestyle{empty}
\mbox{}

\tableofcontents

\chapter{Introduction}
Write introduction

\chapter{Architecture of the underwriter}
Write a section on the architecture of the underwriter application and
rationale for decisions made. As part of this, produce a UML
diagram(s) that shows the architecture of your application. The design
diagram I used for the CSA application discussed in class might be a
useful starting point. I drew mine using Powerpoint, but feel free to use
another tool or even to draw neatly by hand!
\chapter{Architecture of the RESTful broker}
Write a section on the architecture of the RESTful broker client,
providing rationale for decisions made.
\chapter{Test strategy}
Write a section on your test strategy. IMPORTANT: Provide a
screencast of your underwriter application and RESTful broker client
working (some free screen-casting tools can be found online). This
must focus on the broker to underwriter interworking and be no longer
than five minutes long.
\chapter{Self-evaluation}
Write a self-evaluation section. Say what mark you should be awarded
and why. Say what you found hard or easy, and what was omitted and
why. Provide an analysis of your design and the appropriateness, or
otherwise, of the technologies used.

\bibliographystyle{ieeetr}
\bibliography{bibl}

\end{document}